Measuring Political Freedom Around the World

### 2020-11-23 slides.Rmd
usless git commit
rm comment

# Summary Statistics
---

@@

data %>% 
  group_by(polrights_fh) %>% 
  add_count(polrights_fh) %>% 
  ggplot(aes(x = polrights_fh, fill = factor(polrights_fh)), color = "#3C989E") + 
  geom_bar() + 
  geom_text(data = lab, aes(x = polrights_fh, y = n, label = n),
            color = "#3C989E", size = 8, vjust = -.10) + 
  viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
  scale_x_continuous(breaks = 1:7) + 
  theme_test(base_size = 30) + 
#    + 
  theme(legend.position = "none") + 
  labs(y = "Number", x = "Political Freedom", title = "Distribution of Political Freedom")
```

@@

@@

@@

@@

$$
\begin{align}
t(.975; 643) = 1.963
\end{align}
$$
- Conclude error variance is not constant

@@

$$
\begin{align}
{\displaystyle t^{*}_{BF} ={\frac {{\bar {d}}_{1}-{\bar {d}}_{2}}{s^2 {\sqrt {{\frac {1}{n_{1}}}+{\frac {1}{n_{2}}}}}}}}
\end{align}
$$
***

@@

$$
\begin{align}
t(.975; 639) = 1.963
\end{align}
$$
- Conclude again error variance is not constant even when outliers are removed

>>>>

# Summary Statistics

@@

data %>% 
  group_by(polrights_fh) %>% 
  add_count(polrights_fh) %>% 
  ggplot(aes(x = polrights_fh, fill = factor(polrights_fh)), color = "#3C989E") + 
  geom_bar() + 
  geom_text(data = lab, aes(x = polrights_fh, y = n, label = n),
            color = "#3C989E", size = 8, vjust = -.10) + 
  viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
  scale_x_continuous(breaks = 1:7) + 
  theme(legend.position = "none") + 
  labs(y = "Number", x = "Political Freedom", title = "Distribution of Political Freedom")
```

@@

```{r}
data %>% 
  ggplot(aes(x = year, y = polrights_fh)) + 
  geom_col() +
  facet_wrap(~country) + 
  coord_flip() + 
  viridis::scale_fill_viridis(discrete = TRUE, direction = -1) +
  scale_x_continuous(breaks = 1:7) + 
  theme(legend.position = "none")
  theme_light(base_size = 12)
```
---

@@

#### Brown-Forsythe Test

@@

$$
\begin{align}
t(.975; 643) = 1.963
\end{align}
$$
***

@@

- Conclude error variance is not constant

@@

$$
\begin{align}
{\displaystyle t^{*}_{BF} ={\frac {{\bar {d}}_{1}-{\bar {d}}_{2}}{s^2 {\sqrt {{\frac {1}{n_{1}}}+{\frac {1}{n_{2}}}}}}}}
\end{align}
$$
***
$$
\begin{align}
t(.975; 639) = 1.963
\end{align}
$$
***

@@

- Conclude again error variance is not constant even when outliers are removed
